---
title: "Untitled"
output: html_document
---


load packages

```{r}

library(pacman)
p_load(tidyverse, brms, parallel, bayesplot, 
       RColorBrewer, cowplot)
ncores = detectCores()
setwd("C:/Users/95/BayesianDecisionWeights/Code")


```

#### ONE PARAMETER 
function for computing Rottenstreich & Wu/Gonzales

```{r}

## rottenstreich
rottenstreich <- function(a, p){
  w = p**(1-a) / (p**(1-a) + (1-p)**(1-a))
  #return(w)
}

## wu 1996?
wu <- function(a, p){
  w = (p**a / (p**a + (1-p)**a)**(1-a))
}

```

function for estimating params with these functions

```{r}

## use the functions:

est_param <- function(fun, num_a, num_p) {
  
  a = seq(0, 1, by = num_a)
  p = seq(0, 1, by = num_p)
  
  df <- tibble(affect = numeric(),
               probability = numeric(),
               utility = numeric()) 
  
  for(aff in a){
    value = sapply(p, fun, a = aff)
    df = rbind(df, 
               tibble(affect = rep(aff, length(p)), 
                      probability = p, 
                      utility = value))
  }
  
  return(df)
}
  
```

Get the data 

```{r}

rot <- est_param(rottenstreich, 0.1, 0.01)
wuGon <- est_param(rottenstreich, 0.1, 0.01)

```

Function for plotting

```{r}

plotW <- function(df, x, y, group){
  ggplot(df, aes({{x}}, {{y}}, 
                 group = {{group}})) +
    geom_line() +
    labs(x = "p", y = "w(p)") +
    coord_fixed(ratio = 1) +
    theme_minimal()
}

```

Use the plotting function

```{r}

## they are the same.. (it seems): prove it.
p1 <- plotW(rot, probability, utility, affect)
p1 <- plotW(wuGon, probability, utility, affect)
ggsave("../Figures/oneParam.png")

```


### TWO PARAMETERS

Gonzalez Wu 

```{r}

## Gonzalez / Wu 
gonzWu <- function(delta, gamma, p){
  w = (delta * (p ** gamma)) / (delta * (p ** gamma) + (1-p)**gamma)
  #return(w)
}
```


Computing utility over (probability, delta, gamma). 

```{r}

est_param2 <- function(fun, num_delta, num_gamma, num_p) {
  
  delta = seq(0.2, 1.8, by = num_delta)
  gamma = seq(0.2, 1.8, by = num_gamma)
  p = seq(0, 1, by = num_p)
  
  df <- tibble(delta = numeric(),
               gamma = numeric(),
               probability = numeric(),
               utility = numeric()) 
  
  for(g in gamma){
    for(d in delta){
      value = sapply(p, gonzWu, delta = d, gamma = g)
      
      df = rbind(df, 
                 tibble(delta = rep(d, length(p)), 
                        gamma = rep(g, length(p)),
                        probability = p, 
                        utility = value))
  }
  }
  return(df)
}

```

Generate data 

```{r}

two_param <- est_param2(gonzWu, 
                        num_delta = 0.2, 
                        num_gamma = 0.2, 
                        num_p = 0.001)

```

Make them factors: 

```{r}
factor_param <- two_param %>%
  mutate(delta = as_factor(delta),
         gamma = as_factor(gamma))
```

Plotting function

```{r}

plotW <- function(df, vis_param, group_param, value){
df %>%
    filter({{vis_param}} == value) %>%
    ggplot(aes(probability, utility, group = {{group_param}}), 
           color = {{group_param}}) +
    geom_abline(intercept = 0, slope = 1) +
    geom_line() +
    labs(x = "p", y = "w(p)") +
    coord_fixed(ratio = 1) +
    #xlim(0, 1) +
    #ylim(0, 1) +
    theme_minimal()
}

```

Plot them: 
reproducing the plot in 1999.

```{r}

p2 <- plotW(df = two_param, 
      vis_param = gamma, 
      group_param = delta, 
      value = "0.6")

p3 <- plotW(df = two_param, 
      vis_param = delta, 
      group_param = gamma, 
      value = "0.6")

#p2: high gamma = a lot of curvature. 
#p3: high delta = high attractiveness?

```

New function to generate plot of 
what they find. 

```{r}

est_param3 <- function(fun, delta, gamma, num_p) {
  
  p = seq(0, 1, by = num_p)
  
  df <- tibble(delta = numeric(),
               gamma = numeric(),
               probability = numeric(),
               utility = numeric()) 
  
  for(g in gamma){
    for(d in delta){
      value = sapply(p, gonzWu, delta = d, gamma = g)
      
      df = rbind(df, 
                 tibble(delta = rep(d, length(p)), 
                        gamma = rep(g, length(p)),
                        probability = p, 
                        utility = value))
  }
  }
  return(df)
}

```

Generate data

```{r}
delta = c(0.77, 0.77, 0.77)
gamma = c(0.24, 0.34, 0.44) #good

Gonzalez_param <- est_param3(gonzWu, 
                             delta = delta, 
                             gamma = gamma, 
                             num_p = 0.001)

```

Plotting function

```{r}
plotG <- function(df, group_param){
df %>%
    ggplot(aes(probability, utility, group = {{group_param}}), 
           color = {{group_param}}) +
    geom_abline(intercept = 0, slope = 1) +
    geom_line() +
    labs(x = "p", y = "w(p)") +
    #xlim(0, 1) +
    #ylim(0, 1) +
    coord_fixed(ratio = 1) +
    theme_minimal()
}

p4 <- plotG(Gonzalez_param, gamma)
ggsave("../Figures/ourHyp.png")
```

plot grid w. cowplot.

```{r}

## first grid
grid1 <- plot_grid(p2, p3, 
                   labels = c('A', 'B'))

ggsave("../Figures/grid1.png")

```


